### 2021-01-31 research project/sections/Background.tex
rp work

In this paper, we focus on two methods for approximating the value of $\pi$. 
The first by French mathematician François Viète, and another discovered by Madhava of Sangamagrama and 
rediscovered by Swiss mathematician Leibniz. Two methods with different approaches have been chosen for 
comparison, the process for the original discovery of these methods
will be explained. The two methods in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurence in mathematics: Madhava was the first to 
find the series notation of the inverse tangent function and Viète was 
the first mathematician to use and infinite product in calculation.

@@

Madhava is the first mathematician known to have found the series notation for 
the inverse tangent function, in the Kerala school of mathematics of Medieval India 
\cite{amermathmonthly}. One of

@@

\begin{figure}[!ht]
\definecolor{qqwuqq}{rgb}{0,0.39215686274509803,0}
\definecolor{uuuuuu}{rgb}{0.26666666666666666,0.26666666666666666,0.26666666666666666}
\definecolor{xdxdff}{rgb}{0.49019607843137253,0.49019607843137253,1}
\definecolor{qqqqzz}{rgb}{0,0,0.6}
\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=0.7]
\clip(-8.372520930232552,-8.50470697674418) rectangle (7.69259534883721,7.028316279069767);
\draw [shift={(-0.03355999206952884,0)},line width=1pt,color=qqwuqq,fill=qqwuqq,fill opacity=0.10000000149011612] (0,0) -- (0:1.3302325581395344) arc (0:44.77428433325932:1.3302325581395344) -- cycle;
\draw [line width=0.8pt,color=qqqqzz] (0,0) circle (6cm);
\draw [line width=1pt] (4.242640687119286,4.242640687119285)-- (6,0);
\draw [line width=1pt] (6,0)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (4.242640687119286,-4.242640687119285)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-6,0)-- (6,0);
\draw [line width=1pt] (-4.275936263984878,-4.209081736713964)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (-0.03355999206952884,0)-- (5.121320343559643,2.1213203435596424);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (-4.275936263984878,-4.209081736713964);
\begin{scriptsize}
\draw [fill=xdxdff] (4.242640687119286,4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.4772465116279085,4.623665116279071) node {$B$};
\draw [fill=xdxdff] (-4.242640687119285,4.242640687119286) circle (2.5pt);
\draw[color=xdxdff] (-4.295311627906972,4.623665116279071) node {$A$};
\draw [fill=xdxdff] (-4.275936263984878,-4.209081736713964) circle (2.5pt);
\draw[color=xdxdff] (-4.336241860465112,-4.55) node {$C$};
\draw [fill=xdxdff] (6,0) circle (2.5pt);
\draw[color=xdxdff] (6.237246511627907,0.3873860465116302) node {$E$};
\draw [fill=xdxdff] (4.242640687119286,-4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.3772465116279085,-4.5) node {$D$};
\draw[color=black] (5.3595720930232575,2.3111069767441874) node {$H'$};
\draw [fill=xdxdff] (5.12,2.12) circle (2.5pt);
\draw[color=black] (3.947479069767444,-0.615404651162788) node {$H$};
\draw [fill=xdxdff] (4.242640687119286,0) circle (2.5pt);
\draw [fill=xdxdff] (0,0) circle (2.5pt);
\draw[color=uuuuuu] (0.00003720930232879,-0.3464558139534907) node {$O$};
\draw[color=qqwuqq] (1.5325953488372117,0.3873860465116302) node {$\alpha$};
\end{scriptsize}
\end{tikzpicture}
\label{fig:image1}
\caption{Circle with 1 segment from a $n$-gon with point $H$ and 2 
segments from an $2n$-gon, one of which on point $H'$, inscribed in 
a circle of radius $OB$, adapted from (Boris Gourévitch) \cite{borisgourevitch2013}}
\end{figure}

>>>>

In this paper, we focus on two methods for approximating the value of $\pi$. 
The first by French mathematician François Viète, and another discovered by Madhava of Sangamagrama and 
rediscovered by Swiss mathematician Leibniz. Two methods with different approaches have been chosen for 
comparison, the process for original discovery of these methods
will be explained. The two in question are one based on 
the infinite series definition of an inverse trigonometric function 
and one where the value is derived using geometry, by mathematician 
Viète. These two mathematical methods were chosen as they are both 
represent a first occurrence in mathematics: Madhava was the first to 
find the infinite series expansion of the inverse tangent function and Viète was 
the first mathematician to use and infinite product in calculation.

@@

Madhava is the first mathematician known to have found the series notation for 
the inverse tangent function, in the Kerala school of mathematics of Medieval India 
\cite{amermathmonthly}. The research made at the Kerala school was documented by 
many mathematicias of their time, namely the astronomer-mathematician Jyesthadeva 
in his treatise \textit{Yukti-Bhasa} written in the Malayam language \cite{oconnor_robertson_2000}. 
Madhava's infinite series expansion of the inverse tangent function can also be 
found in this treatise in this translation, adapted from (R. C. Gupta 67-70) 
\cite{rc_gupta_mgseries}:

\textit{The first term is the product of the given sine and radius of the desired arc divided 
by the cosine of the arc. The succeeding terms are obtained by a process of 
iteration when the first term is repeatedly multiplied by the square of the 
sine and divided by the square of the cosine. All the terms are then divided by 
the odd numbers 1, 3, 5, ... The arc is obtained by adding and subtracting 
respectively the terms of odd rank and those of even rank. It is laid down that 
the sine of the arc or that of its complement whichever is the smaller should be 
taken here as the given sine. Otherwise the terms obtained by this above iteration 
will not tend to the vanishing magnitude.}

@@

\begin{figure}[!ht]
\definecolor{qqwuqq}{rgb}{0,0.39215686274509803,0}
\definecolor{uuuuuu}{rgb}{0.26666666666666666,0.26666666666666666,0.26666666666666666}
\definecolor{xdxdff}{rgb}{0.49019607843137253,0.49019607843137253,1}
\definecolor{qqqqzz}{rgb}{0,0,0.6}
\begin{tikzpicture}[line cap=round,line join=round,>=triangle 45,x=1cm,y=1cm,scale=0.7]
\clip(-8.372520930232552,-8.50470697674418) rectangle (7.69259534883721,7.028316279069767);
\draw [shift={(-0.03355999206952884,0)},line width=1pt,color=qqwuqq,fill=qqwuqq,fill opacity=0.10000000149011612] (0,0) -- (0:1.3302325581395344) arc (0:44.77428433325932:1.3302325581395344) -- cycle;
\draw [line width=0.8pt,color=qqqqzz] (0,0) circle (6cm);
\draw [line width=1pt] (4.242640687119286,4.242640687119285)-- (6,0);
\draw [line width=1pt] (6,0)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (4.242640687119286,-4.242640687119285)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-6,0)-- (6,0);
\draw [line width=1pt] (-4.275936263984878,-4.209081736713964)-- (4.242640687119286,4.242640687119285);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (4.242640687119286,-4.242640687119285);
\draw [line width=1pt] (-0.03355999206952884,0)-- (5.121320343559643,2.1213203435596424);
\draw [line width=1pt] (-4.242640687119285,4.242640687119286)-- (-4.275936263984878,-4.209081736713964);
\begin{scriptsize}
\draw [fill=xdxdff] (4.242640687119286,4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.4772465116279085,4.623665116279071) node {$B$};
\draw [fill=xdxdff] (-4.242640687119285,4.242640687119286) circle (2.5pt);
\draw[color=xdxdff] (-4.295311627906972,4.623665116279071) node {$A$};
\draw [fill=xdxdff] (-4.275936263984878,-4.209081736713964) circle (2.5pt);
\draw[color=xdxdff] (-4.336241860465112,-4.55) node {$C$};
\draw [fill=xdxdff] (6,0) circle (2.5pt);
\draw[color=xdxdff] (6.237246511627907,0.3873860465116302) node {$E$};
\draw [fill=xdxdff] (4.242640687119286,-4.242640687119285) circle (2.5pt);
\draw[color=xdxdff] (4.3772465116279085,-4.5) node {$D$};
\draw[color=black] (5.3595720930232575,2.3111069767441874) node {$H'$};
\draw [fill=xdxdff] (5.12,2.12) circle (2.5pt);
\draw[color=black] (3.947479069767444,-0.615404651162788) node {$H$};
\draw [fill=xdxdff] (4.242640687119286,0) circle (2.5pt);
\draw [fill=xdxdff] (0,0) circle (2.5pt);
\draw[color=uuuuuu] (0.00003720930232879,-0.3464558139534907) node {$O$};
\draw[color=qqwuqq] (1.5325953488372117,0.3873860465116302) node {$\alpha$};
\end{scriptsize}
\end{tikzpicture}
\label{fig:image1}
\caption[]{Circle with 1 segment from a $n$-gon with point $H$ and 2 
segments from an $2n$-gon, one of which on point $H'$, inscribed in 
a circle of radius $OB$, adapted from (Boris Gourévitch) \cite{borisgourevitch2013}}
\end{figure}

### 2021-01-31 research project/sections/Introduction.tex
rp work

This research could prove useful in the field of computer science, as 
there is always a demand for faster and more efficient programs in an
everchanging society.

>>>>

This research could prove useful in the field of computer science, as 
there is always a demand for faster and more efficient programs in an
ever-changing society.
